\documentclass[12pt,a4paper]{article}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[ruled,linesnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage[colorlinks, linkcolor=blue, anchorcolor=blue, citecolor=green]{hyperref}
\usepackage[table]{xcolor}
\usepackage{subfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{layout}
%\usepackage{ctex}

%\footskip = 10pt
\pagestyle{fancy}
\chead{Group Project}
\lhead{CS7310-Algorithm@SJTU}
\rhead{Instructor: Xiaofeng Gao}
\rfoot{}
\cfoot{Page \thepage \ of \pageref{LastPage}}
\addtolength{\headheight}{0.5\baselineskip}
\addtolength{\headwidth}{0\marginparsep}
\addtolength{\headwidth}{0\marginparwidth}



\title{Scheduling Jobs across Geo-Distributed Data Centers}

\begin{document}

%\linespread{0.85}

The entrypoint of algorithm is \textbf{dfs-solution}. Utilize it to find optimal solutions,
and find guaranteed feasible solutions if scaled too much.

\begin{minipage}[t]{1\textwidth}
	\begin{algorithm}[H] \label{Alg_dfs}
		\KwIn{
			Jobs $J = [j_1, j_2, \cdots, j_n]$,
			Available Partitions $P$,
			Execution Plan $E$ includes a series of jobs.}
		\KwOut{Feasible solutions $S$}
		\caption{dfs-solution}
		\BlankLine

		\textbf{\underline{Found Solution}}

		$t_q = +\infty$
		\tcc*{Total quickest finished jobs series}


		\If{$J = \varnothing$}{
			$t \leftarrow CalculateTime(E)$

			\If {$t < t_q$}{
				$S = \varnothing$

				$t_q \leftarrow t$
			}
			\If {$t = t_q$}{
				$S \overset{+}{\leftarrow} E$
			}
		}

		\BlankLine
		\textbf{\underline{Searching}}

		\For{$j_i$ in $J$}{
			\If {$dependences[j_i] \in P$} {
				$L = Heuristic(j_i, P, E)$
				\tcc*{Ordered slots for job to be executed}

				\For{$l_k$ in $L$}{
					dfs-solution($P+j_i$, $J-j_i$, $E+e_{j_i,l_k}$) 
				}
			}
		}
	\end{algorithm}
\end{minipage}


\begin{minipage}[t]{1\textwidth}
	\begin{algorithm}[H] \label{Alg_heuristic}
		\KwIn{
			All available slots $L = [l_1, l_2, \cdots, l_m]$ in each datacenter(one for each),
			Job $j$,
			Available Partitions $P$,
			Execution Plan $E$ includes a series of jobs.}
		\KwOut{Ordered slots $L^\star$}
		\caption{Heuristic}
		\BlankLine

		\For{$l_k$ in $L$}{
			$m \leftarrow [\text{data center contains same main job} , \text{data center contains main job partitions}]$

			$w_k=
				\begin{cases}
					3 & \text{if } m = [true, true]\\
					2 & \text{if } m = [true, false]\\
					1 & \text{if } m = [false, false]\\
					0 & \text{else}\\
				\end{cases}
			$
		}

		$L^\star \leftarrow SORT(L, W)$
		\tcc*{Sort slots by weight $W = [w_1, \cdots, w_m]$}

		\Return{$L^\star$}
	\end{algorithm}
\end{minipage}


\begin{minipage}[t]{1\textwidth}
	\begin{algorithm}[H] \label{Alg_calctime}
		\KwIn{
			Jobs $J = [j_1, j_2, \cdots, j_n]$,
			Available Partitions $P$,
			Execution Plan $E \in J$ includes a series of jobs.}
		\KwOut{Time $t$}
		\caption{CalculateTime}
		\BlankLine

		$R_f \leftarrow \varnothing$

		\For{$j_i$ in $J$}{
			$td_{i} \leftarrow 0$

			\For {$d_{j_i,k}$ in $dependences[j_i]$} {
				\If{$DC[d_{j_i,k}] \neq DC[j_i]$}{
					$LINKS \leftarrow ShortestPath(DC[d_{j_i,k}], DC[j_i])$

					$td_{i} \leftarrow \sum_{l_h \in LINKS} Time[l_h]$
				}
			}

			$avail[j_i] \overset{+}{\leftarrow} td_i+duration[j_i]$
			
			$R_f \overset{+}{\leftarrow} avail[j_i]$
		}

		$t \leftarrow \max_{r_{f,i} \in R_f} r_{f,i}$

		\Return{$L^\star$}
	\end{algorithm}
\end{minipage}

\textbf{Optimal Solution. } If we want to find the optimal solution,
and let the \textbf{dfs} algorithm finish all possibilities,
the complexity is $O(n!m!)$,
which $n$ is number of jobs, $m$ is total slot number of all datacenters.

\par
\textbf{Approximation Solution. } If we just want to find the approximation solution,
which guaranteed at least feasible,
the complexity is $O(nm + m \log m)$,
which $n$ is number of jobs, $m$ is total slot number of all datacenters.

\end{document}
